---
title: "Mancala Board Game"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Through this article, I am going to explian the technology stack which I used to create Mancala web game, I will explore some code snippts and the internal system archtict. Also, you will find a demo vedio about how you can play.

For more information about Mancala board game <https://en.wikipedia.org/wiki/Kalah>.

##1. Project Environment
* Spring Tool Suite 3.8.2.RELEASE
* JDK 1.8
* Apache Maven 3.3.9
* WebSocket (STOMP)

##2. Project Package Structure
* src/main/java
    + com.backbase.mancala
        + MancalaApplication.java
        + MancalaApplication.java
    + com.backbase.mancala.controller
        + ChatController.java
        + GameController.java
    + com.backbase.mancala.domain
        + Pebble.java
        + Pile.java
    + com.backbase.mancala.dto
        + GameBoard.java
        + GameStatus.java (Enum)
        + Message.java 
        + Winner.java (Enum)
    + com.backbase.mancala.service
        + IBoardGame.java
        + MancalaGame.java
* src/main/resource
    + static
        + app.js
        + index.html
        + main.css
* src/main/test
    + com.backbase.mancala
        + MancalaApplicationTests.java
        
##3. Project Class Diagram

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
